\runsubsection{Natwest Ventures - Mettle}
\descript{| Cloud Platform \& Security Engineer}
\location{August 2020 – February 2022 | Perm}
\sectionsep
\textbf{Technology}: AWS, Confluence, Datadog, Docker, Github, Jira, Hashicorp, IdP, K8s, Kafka, Linux (Flatcar, Bottlerocket), Nginx, PagerDuty, Sumologic, Sysdig, Snyk
\sectionsep
\begin{tightemize}
\item Work closely with architects and engineers to develop security guardrails for cloud native services and solutions.
\item Continuously improving detection and visibility for security events across cloud infrastructure and used SaaS.
\item Help to refactor and redesign the observability of the system (by unifying metrics, logs, traces and alerting).
\item Ensure infrastructure are robust, value for money and continuously optimised.
\item Work with mission teams to provide a self-service platform (leveraging Github PRs and Actions).
\end{tightemize}
\sectionsep
\sectionsep
\runsubsection{Natwest Ventures - Bó}
\descript{| Site Reliability Engineer}
\location{April 2019 – August 2020 | Contract -> Perm}
\sectionsep
\textbf{Technology}: AWS, Confluence, Datadog, Docker, Github, Jira, Hashicorp, K8s, LDAP, Linux (Amzn, CoreOS), Nginx, Packer, PagerDuty, Squid (Egress Proxy), VPN
\sectionsep
\begin{tightemize}
\item Delivering continuous improvement to the cloud platform security while balancing security against other business requirements.
\item Contribute to the code base (infrastructure as code) and make sure that it is clean, elegant, reusable, and easy to maintain and extend.
\item Collaborated with the wider organisation to produce blameless postmortems tolearn and share lessons from incidents.
\item Decommission of company's infrastructure and ensuring operational data is encrypted and archived for auditing purposes.
\item Built self-service observability and alerting capability around structured logging, metrics and distributed tracing, helping engineering teams to create their own dashboards and alerts.
\end{tightemize}
\sectionsep
\sectionsep
\runsubsection{RS Components}
\descript{| Site Reliability Engineer}
\location{January 2018 – March 2019 | Contract}
\sectionsep
\textbf{Technology}: Artifactory, Ansible, AWS, Confluence, Consul, Datadog, Docker, GitLab, Jenkins, Jira, Kong, LDAP, Linux (Amzn, Ubuntu), Nginx, Nomad, OpenVPN, Sonar, Terraform, Terragrunt, Vault
\sectionsep
\begin{tightemize}
\item Assist with the transformation project - working alongside engineering teams to decompose monolith systems into manageable microservices.
\item Ensure all services go through a deterministic delivery pipeline via a highly available CI system.
\item Building and solving challenges in networking, security, speed, scalability, resilience and recoverability.
\end{tightemize}
\sectionsep

\end{minipage}
\hfill
\begin{minipage}[t]{0.25\textwidth}

\section{Skills}\label{sec:skills}
\subsection{Programming}\label{subsec:programming}
\sectionsep
\location{Proficient:}
CSS3
\textbullet{} Golang
\textbullet{} HCL2 \\
HTML
\textbullet{} Shell \\
\sectionsep
\location{Experienced:}
C\#
\textbullet{} Java
\textbullet{} JavaScript \\
Python
\textbullet{}  SQL \\
\sectionsep
\location{Familiar:}
C++
\textbullet{} PHP
\textbullet{} Perl
\sectionsep
\sectionsep
\subsection{Libraries/Frameworks}\label{subsec:libraries/frameworks}
\sectionsep
Django
\textbullet{} HTTP/TCP/IP
\textbullet{} JSON \\
JQ
\textbullet{} jQuery
\textbullet{} OIDC / SAML \\
Serverless
\textbullet{} Terraform \\
Terragrunt
\textbullet{} YAML
\sectionsep
\sectionsep
\subsection{Tools/Platforms}\label{subsec:tools/platforms}
\sectionsep
Ansible
\textbullet{} Atlantis
\textbullet{} AWS \\
Bazel
\textbullet{} Boundary
\textbullet{} Consul \\
Datadog
\textbullet{} Docker
\textbullet{} Git \\
Github/GitLab (CI)
\textbullet{} Grafana \\
Kafka
\textbullet{} Kaniko
\textbullet{} Kubernetes \\
Nginx
\textbullet{} Nomad
\textbullet{} Onelogin \\
OpenLDAP
\textbullet{} OpenVPN \\
Packer
\textbullet{} PagerDuty \\
Prometheus
\textbullet{} Snyk \\
Sumologic
\textbullet{} Sysdig
\textbullet{} Vault
\sectionsep
\subsection{Operating Systems}\label{subsec:operating-systems}
\sectionsep
Linux
\textbullet{} Mac
\textbullet{} Windows \\
Daily Driver: NixOS (Linux)

\section{Education}\label{sec:education}
\subsection{The Univ. of Edinburgh}\label{subsec:the-university-of-edinburgh}
\descript{BSc. Computer Science}
\location{2001 - 2006, 1st Class | Edinburgh, U.K.}
Core Curricula: Computer Science, Artificial Intelligence \& Discrete Mathematics \\
Honors Project: Design and Evaluation of a Transparently Pipe-lined Microprocessor

\section{Internship}\label{sec:internship}
\subsection{ARC International}\label{subsec:arc-international}
\descript{Application (Hardware) Engineer}
\location{June 2005 - September 2005}
Self-managed project on porting the EEMBC benchmark (GNU C) and to provide a performance evaluation for ARC’s latest configurable processors (embedded) - ARC 700 and 600 core family.

\end{minipage}

\begin{minipage}[t]{1.0\textwidth}
\runsubsection{Wickes}
\descript{| DevOps Engineer}
\location{May 2017 – September 2017 | Contract}
\sectionsep
\textbf{Technology}: AWS, Confluence, Datadog, Docker, Github, Jira, Hashicorp, K8s, LDAP, Linux (Amzn, CoreOS)
\sectionsep
\begin{tightemize}
\item Focused on capability development where the primary objectives were to deploy, customize and maintain the tools around release, configuration and environment management.
\end{tightemize}
\sectionsep
\sectionsep
\runsubsection{Argos, Kingfisher, Newlook}
\descript{| DevOps Engineer}
\location{May 2015 – January 2017 | Contract}
\sectionsep
\textbf{Technology}: AWS, Confluence, Datadog, Docker, Github, Jira, Hashicorp, K8s, LDAP, Linux (Amzn, CoreOS)
\sectionsep
\begin{tightemize}
\item Collaborated in a multi-client engagement and with multiple teams responsible for everything DevOps and AWS\@.
\end{tightemize}
\sectionsep
\sectionsep
\runsubsection{Towers Watson}
\descript{| Release Engineer \& Software Developer in Test}
\location{August 2012 – August 2014 | Perm}
\sectionsep
\textbf{Technology}: AWS, Confluence, Datadog, Docker, Github, Jira, Hashicorp, K8s, LDAP, Linux (Amzn, CoreOS)
\sectionsep
\begin{tightemize}
\item Part of highly cohesive team responsible for developing the next generation financial modeling tool; performing a software developer in test (emphasis on GUI automation testing) and build engineering role within an agile environment.
\end{tightemize}
\sectionsep
\sectionsep
\runsubsection{Clouco.com}
\descript{| Software Engineer}
\location{May 2011 – May 2015 | Co-Creator}
\sectionsep
\textbf{Technology}: AWS, Confluence, Datadog, Docker, Github, Jira, Hashicorp, K8s, LDAP, Linux (Amzn, CoreOS), Nginx, Packer, PagerDuty, Squid (Egress Proxy), VPN
\sectionsep
\begin{tightemize}
\item Co-founded and co-developed, Clouco is an online address book application where users can share their contact information with friends, family and colleagues.
\end{tightemize}
\sectionsep
\sectionsep
\runsubsection{Rabobank}
\descript{| Release \& Configuration Engineer}
\location{December 2010 – May 2012 | Perm}
\sectionsep
\textbf{Technology}: AWS, Confluence, Datadog, Docker, Github, Jira, Hashicorp, K8s, LDAP, Linux (Amzn, CoreOS), Nginx, Packer, PagerDuty, Squid (Egress Proxy), VPN
\sectionsep
\begin{tightemize}
\item Operated within the context of the IS\&D Global Systems Support Strategy to provide high-quality, efficient and consistent level of service in development, test and support.
\end{tightemize}
\sectionsep
\sectionsep
\runsubsection{Bank of America Merrill Lynch}
\descript{| Data Analyst}
\location{June 2010 – November 2010 | Accenture Consultant}
\sectionsep
\textbf{Technology}: AWS, Confluence, Datadog, Docker, Github, Jira, Hashicorp, K8s, LDAP, Linux (Amzn, CoreOS), Nginx, Packer, PagerDuty, Squid (Egress Proxy), VPN
\sectionsep
\begin{tightemize}
\item The engagement focused on proposing and implementing a structured database for trade migration reconciliation testing, eradicating the use of stacking number of Excel sheets, and consequently increasing the efficiency in reporting defects.
\end{tightemize}
\sectionsep
\sectionsep
\runsubsection{EDF Energy}
\descript{| Release \& Configuration Engineer}
\location{September 2008 – April 2010 | Accenture Consultant}
\sectionsep
\textbf{Technology}: AWS, Confluence, Datadog, Docker, Github, Jira, Hashicorp, K8s, LDAP, Linux (Amzn, CoreOS), Nginx, Packer, PagerDuty, Squid (Egress Proxy), VPN
\sectionsep
\begin{tightemize}
\item Performed technical role within the Development Architecture team to support development and testing.
\end{tightemize}
\sectionsep
\sectionsep
\runsubsection{Department of Work \& Pensions}
\descript{| Release \& Configuration Engineer}
\location{May 2005 – September 2008 | Accenture Consultant}
\sectionsep
\textbf{Technology}: AWS, Confluence, Datadog, Docker, Github, Jira, Hashicorp, K8s, LDAP, Linux (Amzn, CoreOS), Nginx, Packer, PagerDuty, Squid (Egress Proxy), VPN
\sectionsep
\begin{tightemize}
\item Administered configuration management and promoted best practices across the CM landscape, including automation of tasks where possible via applicable technology and documentation of procedures and guides.
\end{tightemize}

\section{Recent Awards}\label{sec:awards}
\begin{tabular}{rll}
2021 & Mettle Hackathon Best Team Presentation Award \\
2021 & Mettle Hackathon $2^{nd}$ Place
\end{tabular}
\end{minipage}